---
title: "RWorksheet_Group5WS"
author: "Sadural,Gregorio,Ulgasan,Fermano,Lomugda"
output: pdf_document
date: "2023-12-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)

url <- "https://www.imdb.com/chart/tvmeter/?ref_=nv_tvv_mptv"

session <- bow(url, user_agent = "For Educational Purpose")
session

# SCRAPE FOR RANK
ranks <- scrape(session) %>%
    html_nodes("div.sc-94da5b1b-0.soBIM.meter-const-ranking.sc-479faa3c-6.glWBvR.cli-meter-title-header") %>%
    html_text
ranks50 <- ranks[1:50]
ranks50 <- substr(ranks50, 1, 2)
ranks50


# SCRAPE FOR TITLE
title <- scrape(session) %>%
    html_nodes("h3.ipc-title__text") %>%
    html_text
title50 <- title[2:51]
title50


# SCRAPE FOR TV RATING
tv_rating <- scrape(session) %>%
    html_nodes("span.ipc-rating-star.ipc-rating-star--base.ipc-rating-star--imdb.ratingGroup--imdb-rating:contains('.')") %>%
    html_text
tv_rating50 <- tv_rating[1:50]
tv_rating50only <- substr(tv_rating50, 1, 3)
tv_rating50only


# SCRAPE FOR NUMBER OF VOTES
num_votes <- scrape(session) %>%
    html_nodes("span.ipc-rating-star--voteCount") %>%
    html_text
num_votes50 <- num_votes[1:50]
num_votes50


# SCRAPE FOR NUMBER OF EPISODES
num_eps <- scrape(session) %>%
    html_nodes("span.sc-479faa3c-8.bNrEFi.cli-title-metadata-item:contains('eps')") %>%
    html_text %>%
  gsub("\\D", "", .)
num_eps50 <- num_eps[1:50]
num_eps50


# SCRAPE FOR YEAR RELEASED
year_released <- scrape(session) %>%
    html_nodes("span.sc-479faa3c-8.bNrEFi.cli-title-metadata-item:contains('20')") %>%
    html_text
year_released50 <- year_released[1:50]


# CREATE DATAFRAME
tv_series_data <- data.frame(
  Rank = ranks50,
  Title = title50,
  TV_Rating = tv_rating50only,
  Num_Votes = num_votes50,
  Num_Episodes = num_eps50,
  Year_Released = year_released50
)

View(tv_series_data)
  
```

2. From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the
reviewer’s name, date of reviewed, user rating, title of the review, and text reviews.

```{r}

link_of_list <- scrape(session) %>%
  html_nodes('a.ipc-title-link-wrapper') %>%
  html_attr('href')

link_of_list5 <- link_of_list[1:5]

for (i in 1:5) {
 link_of_list5[i] <- paste0("https://imdb.com", link_of_list5[i], sep = "")
}

link_of_list5
```

```{r}
library(stringr)

split_links <- strsplit(link_of_list5, "/")
split_links

unique_ids <- sapply(split_links, function(link) {
  
  id_part <- grep("tt[0-9]+", link, value = TRUE)
  
  if (length(id_part) > 0) {
    return(id_part)
  } else {
    return(NA)
  }
})

# Pasting the Unique ID to imdb site to access the review section
for (i in 1:5) {
 unique_ids[i] <- paste0("https://imdb.com/title/",unique_ids[i],"/reviews?ref_=tt_urv", sep = "") }

unique_ids

```



```{r}

rowrow <- 1
put <- 1

review_list <- list()
rank_one_review <- data.frame()
rank_two_review <- data.frame()
rank_three_review <- data.frame()
rank_four_review <- data.frame()
rank_five_review <- data.frame()

for (rowrow in 1:5){
  
  url  <- unique_ids[rowrow]
  session2 <- bow(url, user_agent = "abdul's education")
  webpage <- scrape(session2)
  
  nameofreviewer <- html_text(html_nodes(webpage,"span.display-name-link"))
  nameofreviewer5 <- nameofreviewer[1:5]
  nameofreviewer5

  date_of_review <- html_text(html_nodes(webpage,"span.review-date"))
  date_of_review5 <- date_of_review[1:5]
  date_of_review5
   
  user_rating <- html_text(html_nodes(webpage,"span.rating-other-user-rating"))
  user_rating5 <-  user_rating[1:5]
  user_rating5
   
   
  title_of_review <- html_text(html_nodes(webpage,"a.title"))
  title_of_review5 <- title_of_review[1:5]
  title_of_review5
  
  text_review <- html_text(html_nodes(webpage,"div.text.show-more__control"))
  text_review5 <- text_review[1:5]
  text_review5


  for(put in 1:5){
  
    if(rowrow == 1){
    
      rank_one_review[put, 1] <- nameofreviewer5[put]
      rank_one_review[put, 2] <- date_of_review5[put]
      rank_one_review[put, 3] <- user_rating5[put]
      rank_one_review[put, 4] <- title_of_review5[put]
      rank_one_review[put, 5] <- text_review5[put]
      
    
    } else if(rowrow == 2){
      
      rank_two_review[put, 1] <- nameofreviewer5[put]
      rank_two_review[put, 2] <- date_of_review5[put]
      rank_two_review[put, 3] <- user_rating5[put]
      rank_two_review[put, 4] <- title_of_review5[put]
      rank_two_review[put, 5] <- text_review5[put]
      
    
    }else if(rowrow == 3){
    
      rank_three_review[put, 1] <- nameofreviewer5[put]
      rank_three_review[put, 2] <- date_of_review5[put]
      rank_three_review[put, 3] <- user_rating5[put]
      rank_three_review[put, 4] <- title_of_review5[put]
      rank_three_review[put, 5] <- text_review5[put]
    
    }else if(rowrow == 4){
    
      rank_four_review[put, 1] <- nameofreviewer5[put]
      rank_four_review[put, 2] <- date_of_review5[put]
      rank_four_review[put, 3] <- user_rating5[put]
      rank_four_review[put, 4] <- title_of_review5[put]
      rank_four_review[put, 5] <- text_review5[put]
      
    }else if(rowrow == 5){
      
      rank_five_review[put, 1] <- nameofreviewer5[put]
      rank_five_review[put, 2] <- date_of_review5[put]
      rank_five_review[put, 3] <- user_rating5[put]
      rank_five_review[put, 4] <- title_of_review5[put]
      rank_five_review[put, 5] <- text_review5[put]
      
     }
  }
  
  rowrow <- rowrow + 1
}  


```


3. Create a time series graph for the tv shows released by year. Which year has the most number of tv
shows released?

```{r}

tv_series_dataa <- tv_series_data %>%
  mutate(Start_Year = as.numeric(str_extract(Year_Released, "\\b\\d{4}\\b"))) %>%
  filter(!is.na(Start_Year))


ggplot(tv_series_dataa, aes(x = Start_Year)) +
  geom_bar(stat = "count", fill = "black") +
  labs(title = "Number of TV Shows Released by Year",
       x = "Start Year of the TV Show",
       y = "Number of TV Shows") +
  theme_minimal()


```
4. Select 3 products from Amazon of the same category. Extract the price, description, ratings and
reviews of each product.
```{r}


url <- "https://www.amazon.com/SteelSeries-Apex-Hybrid-Mechanical-Gaming-Keyboard/dp/B07ZGDD6B1/ref=sr_1_1_sspa?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&keywords=gaming%2Bkeyboard&pd_rd_r=37d1ea2c-8e88-4495-be67-37d3b5a3d1d1&pd_rd_w=pDPnL&pd_rd_wg=vVF4U&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=MDA7C7ZE453N7YHK4TZK&qid=1701532564&sr=8-1-spons&sp_csd=d2lkZ2V0TmFtZT1zcF9hdGY&th=1"

session4a <- bow(url,
               user_agent = "For Educational Purpose")
session4a

product_name <- scrape(session4a) %>%
                html_nodes("span.a-size-large.product-title-word-break") %>%
                html_text
product_name

product_price <- scrape(session4a) %>%
    html_nodes("div.a-section.a-spacing-none.aok-align-center") %>%
    html_text
product_price

product_description <- scrape(session4a) %>%
    html_nodes("div.a-expander-collapsed-height.a-row.a-expander-container.a-spacing-none.a-expander-partial-collapse-container") %>%
    html_text
product_description

product_ratings <- scrape(session4a) %>%
    html_nodes("span.a-size-base.a-color-base") %>%
    html_text
product_ratings


```

```{r}

```  
