---
title: "RWorksheet_Group5WS"
author: "Sadural,Lomugda,Ulgasan,Fermano,Gregorio"
output: pdf_document
date: "2023-12-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

install.packages("dplyr")
install.packages("rvest")
install.packages("httr")
install.packages("polite")
install.packages("ggplot2")
library(rvest)
library(httr)
library(dplyr)
library(polite)
library(ggplot2)
```
1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.


```{r}
library(polite)
library(rvest)
library(httr)
library(dplyr)



url_link <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250"
session <- bow(url_link, user_agent= "Educational Purposes")
session

#rank of the Top 50 Tv Shows
TV_rank <- scrape(session)  %>% html_nodes('h3.ipc-title__text') %>% html_text()
TV_rank [1:51]


#Titles of the Top 50 Tv Shows
TV_title <- scrape(session) %>%
    html_nodes('h3.ipc-title__text') %>%
    html_text()
TV_title [1:51]

#Rating of the Top 50 Tv Shows
TV_rating <- scrape(session) %>%
    html_nodes('span.ipc-rating-star--imdb') %>%
    html_text()
TV_rating [1:51]

#Numbers Of Voters of the Top 50 Tv Shows
numberofTV_voters <- scrape(session) %>%
    html_nodes('span.ipc-rating-star--imdb') %>%
    html_text()
numberofTV_voters [1:51]

#This shows on how many Episodes does the Top 50 Tv Shows have
TV_episodes <- scrape(session) %>%
    html_nodes('span.ipc-rating-star--voteCount') %>%
    html_text()
TV_episodes [1:51]

#The Year it was released (The Top 50 Tv Shows)
year <- scrape(session) %>%
    html_nodes('span.sc-479faa3c-8:nth-of-type(1)') %>%
    html_text()
year [1:51]
mini_length <- min(length(TV_rank), length(TV_title), length(TV_rating), length(numberofTV_voters), length(TV_episodes), length(year))
mini_length

TV_shows_data <- data.frame(
  Rank = seq(1, mini_length),
  Title = TV_title[1:mini_length],
  Rating = TV_rating[1:mini_length],
  NumberOfVoters = numberofTV_voters[1:mini_length],
  Episodes = TV_episodes[1:mini_length],
  Year = (sapply(year[1:mini_length], function(x) if (grepl("^\\d+$", x)) as.integer(x) else NA))
)

View(TV_shows_data)
```

2. From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the
reviewer’s name, date of reviewed, user rating, title of the review, and text reviews.

```{r}

firstreviewlink <- "https://www.imdb.com/title/tt0903747/reviews?ref_=tt_urv"
session_1 <- bow(firstreviewlink, user_agent= "Educational Purposes")
session_1

Reviewers_Nametv1 <- scrape(session_1) %>%
    html_nodes('.display-name-link a') %>%
    html_text()
Reviewers_Nametv1

Reviews_Datetv1 <- scrape(session_1) %>%
    html_nodes('.review-date') %>%
    html_text()
Reviews_Datetv1

User_Ratingtv1 <- scrape(session_1) %>%
    html_nodes('.rating-other-user-rating') %>%
    html_text()
User_Ratingtv1

Rev_Titletv1 <-scrape(session_1) %>%
    html_nodes('.parent a') %>%
    html_text()
Rev_Titletv1

Text_Revtv1 <-scrape(session_1) %>%
    html_nodes('.collapsable div.text') %>%
    html_text()
Text_Revtv1


secondreviewlink <- "https://www.imdb.com/title/tt5491994/reviews?ref_=tt_urv"
session_2 <- bow(secondreviewlink, user_agent= "Educational Purposes")
session_2

Reviewers_Nametv2 <- scrape(session_2) %>%
    html_nodes('.display-name-link a') %>%
    html_text()
Reviewers_Nametv2

Reviews_Datetv2 <- scrape(session_2) %>%
    html_nodes('.review-date') %>%
    html_text()
Reviews_Datetv2

User_Ratingtv2 <- scrape(session_2) %>%
    html_nodes('.rating-other-user-rating') %>%
    html_text()
User_Ratingtv2

Rev_Titletv2 <-scrape(session_2) %>%
    html_nodes('.parent a') %>%
    html_text()
Rev_Titletv2

Text_Revtv2 <-scrape(session_2) %>%
    html_nodes('.collapsable div.text') %>%
    html_text()
Text_Revtv2


thirdreviewlink <- "https://www.imdb.com/title/tt0185906/reviews?ref_=tt_urv"
session_3 <- bow(thirdreviewlink, user_agent= "Educational Purposes")
session_3

ReviewersNametv3 <- scrape(session_3) %>%
    html_nodes('.display-name-link a') %>%
    html_text()
ReviewersNametv3

ReviewsDatetv3 <- scrape(session_3) %>%
    html_nodes('.review-date') %>%
    html_text()
ReviewsDatetv3

UserRatingtv3 <- scrape(session_3) %>%
    html_nodes('.rating-other-user-rating') %>%
    html_text()
UserRatingtv3

RevTitletv3 <-scrape(session_3) %>%
    html_nodes('.parent a') %>%
    html_text()
RevTitletv3

TextRevtv3 <-scrape(session_3) %>%
    html_nodes('.collapsable div.text') %>%
    html_text()
TextRevtv3


fourthreviewlink <- "https://www.imdb.com/title/tt7366338/reviews?ref_=tt_urv"
session4 <- bow(fourthreviewlink, user_agent= "Educational Purposes")
session4

Reviewers_Nametv4 <- scrape(session4) %>%
    html_nodes('.display-name-link a') %>%
    html_text()
Reviewers_Nametv4

Reviews_Datetv4 <- scrape(session4) %>%
    html_nodes('.review-date') %>%
    html_text()
Reviews_Datetv4

User_Ratingtv4 <- scrape(session4) %>%
    html_nodes('.rating-other-user-rating') %>%
    html_text()
User_Ratingtv4

Rev_Titletv4 <-scrape(session4) %>%
    html_nodes('.parent a') %>%
    html_text()
Rev_Titletv4

Text_Revtv4 <-scrape(session4) %>%
    html_nodes('.collapsable div.text') %>%
    html_text()
Text_Revtv4

#fifth
fifthreviewlink <- "https://www.imdb.com/title/tt2395695/reviews?ref_=tt_urv"
session5 <- bow(fifthreviewlink, user_agent= "Educational Purposes")
session5

Reviewers_Nametv5 <- scrape(session5) %>%
    html_nodes('.display-name-link a') %>%
    html_text()
Reviewers_Nametv5

Reviews_Datetv5 <- scrape(session5) %>%
    html_nodes('.review-date') %>%
    html_text()
Reviews_Datetv5

User_Ratingtv5 <- scrape(session5) %>%
    html_nodes('.rating-other-user-rating') %>%
    html_text()
User_Ratingtv5

Rev_Titletv5 <-scrape(session5) %>%
    html_nodes('.parent a') %>%
    html_text()
Rev_Titletv5

Text_Revtv5 <-scrape(session5) %>%
    html_nodes('.collapsable div.text') %>%
    html_text()
Text_Revtv5


```

3. Create a time series graph for the tv shows released by year. Which year has the most number of tv
shows released?
```{r}
library(ggplot2)
library(dplyr)

ggplot(data, aes(x = Year, fill = factor(Year))) +
  geom_bar() +
  labs(title = "Number of TV Shows Released by Year",
       x = "Year",
       y = "Number of TV Shows") +
  theme_minimal()

most_shows_year <- data %>%
  group_by(Year) %>%
  summarize(NumShows = n()) %>%
  arrange(desc(NumShows)) %>%
  slice(1)

cat("Year with the most TV shows released:", most_shows_year$Year, "\n")
cat("Number of TV shows released:", most_shows_year$NumShows, "\n")



```

4. Select 3 products from Amazon of the same category. Extract the price, description, ratings and
reviews of each product.

```{r}
#1stproduct
url <- "https://www.amazon.com/SteelSeries-Apex-Hybrid-Mechanical-Gaming-Keyboard/dp/B07ZGDD6B1/ref=sr_1_1_sspa?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&keywords=gaming%2Bkeyboard&pd_rd_r=37d1ea2c-8e88-4495-be67-37d3b5a3d1d1&pd_rd_w=pDPnL&pd_rd_wg=vVF4U&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=MDA7C7ZE453N7YHK4TZK&qid=1701532564&sr=8-1-spons&sp_csd=d2lkZ2V0TmFtZT1zcF9hdGY&th=1"

session4 <- bow(url,
               user_agent = "For Educational Purpose")
session4

product_name <- scrape(session4) %>%
                html_nodes("span.a-size-large.product-title-word-break") %>%
                html_text
product_name

product_price <- scrape(session4) %>%
    html_nodes("div.a-section.a-spacing-none.aok-align-center") %>%
    html_text
product_price

product_description <- scrape(session4) %>%
    html_nodes("div.a-expander-collapsed-height.a-row.a-expander-container.a-spacing-none.a-expander-partial-collapse-container") %>%
    html_text
product_description

product_ratings <- scrape(session4) %>%
    html_nodes("span.a-size-base.a-color-base") %>%
    html_text
product_ratings



#2ndproduct

amazonlink2nd <- "https://www.amazon.com/dp/B09S5MJLF6/ref=sspa_dk_detail_2?psc=1&pd_rd_i=B09S5MJLF6&pd_rd_w=tkc0I&content-id=amzn1.sym.386c274b-4bfe-4421-9052-a1a56db557ab&pf_rd_p=386c274b-4bfe-4421-9052-a1a56db557ab&pf_rd_r=AFCCC2P8F4VENZZF4VRZ&pd_rd_wg=GH9kV&pd_rd_r=585deed2-ce5f-497b-b3f1-dbc0ea621f62&s=wireless&sp_csd=d2lkZ2V0TmFtZT1zcF9kZXRhaWxfdGhlbWF0aWM&spLa=ZW5jcnlwdGVkUXVhbGlmaWVyPUEyQzFIRDc2SUVHRlU5JmVuY3J5cHRlZElkPUEwMzMxNzg1MlBaVzRHV042M0hSNyZlbmNyeXB0ZWRBZElkPUEwODMzMDgyMUhUNlhSRVNSTlM3RCZ3aWRnZXROYW1lPXNwX2RldGFpbF90aGVtYXRpYyZhY3Rpb249Y2xpY2tSZWRpcmVjdCZkb05vdExvZ0NsaWNrPXRydWU="

session7 <- bow(amazonlink2nd, user_agent= "Educational Purposes")
session7


price2 <-scrape(session7) %>%
    html_nodes('#corePriceDisplay_desktop_feature_div .a-price-whole') %>%
    html_text()
price2

description2 <-scrape(session7) %>%
    html_nodes('#feature-bullets .a-list-item') %>%
    html_text()
description2

prodrating2 <-scrape(session7) %>%
    html_nodes('#acrPopover') %>%
    html_text()
prodrating2

prodreview2 <- scrape(session7) %>%
    html_nodes('#acrPopover') %>%
    html_text()
prodreview2


```